The SMT Competition 2015--2018

### 2019-08-27 2018/report/SMT-COMP.tex
Minor
Clarify that we list team members as reported by the development teams

Tables~\ref{table:participants1}--\ref{table:participants3} list the solvers
that participated between~2015 and~2018, together with contributing team
members (in alphabetical order) and their institutional affiliations (which may
have changed over time).

@@

The \emph{(weighted) score} of a solver in a (\maintrack or
\ucoretrack) division~$D$ is then defined as the weighted sum of all
raw scores
%
$$\sum_{b\in D} \alpha'_b \cdot \langle e_b \cdot |D|, n_b \cdot |D|, w_b,
  c_b\rangle$$
%
where the sum is over all benchmarks in the division, and~$|D|$ is the
number of benchmarks in~$D$.  This is computed separately for parallel
and sequential performance.

>>>>

Tables~\ref{table:participants1}--\ref{table:participants3} list the solvers
that participated between~2015 and~2018, together with contributing team
members (in alphabetical order) and their institutional affiliations (which may
have changed over time) as reported by the development teams.

@@

The \emph{(weighted) score} of a solver in a (\maintrack or
\ucoretrack) division~$D$ is then defined as the weighted sum of all
raw scores
%
$$\sum_{b\in D} \alpha'_b \cdot \langle e_b \cdot |D|, n_b \cdot |D|, w_b,
  c_b\rangle$$
%
where the sum is over all benchmarks in the division, and~$|D|$ is the
number of benchmarks in~$D$.  This is computed separately for parallel
and sequential scores.
